%!TEX program = lualatex
\documentclass[11pt, letterpaper]{article}

% ======================================================================
% 1. CORE PACKAGES & GEOMETRY
% ======================================================================
\usepackage[letterpaper, margin=.6in, includefoot, footskip=0.3in]{geometry}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{unicode-math}
\usepackage{longtable} 
\usepackage{booktabs}  
\usepackage{tikz}

% Define ALQC Colors
\definecolor{voidblack}{HTML}{050505}
\definecolor{sovereignfire}{HTML}{CC3300}

% ======================================================================
% 2. FONT CONFIGURATION (Standard Canvas Noto Family)
% ======================================================================
\setmainfont{Noto Sans}
\setmathfont{Latin Modern Math}

\newfontfamily\tibetanfont{Noto Serif Tibetan}[Scale=1.0]
\newfontfamily\symbolsfont{Noto Sans Symbols}[Scale=1.0]
\newfontfamily\thaanafont{Noto Sans Thaana}[Scale=1.0]

% ======================================================================
% 3. OPERATOR & GLYPH DEFINITIONS (Hard-Typed Standard)
% ======================================================================
\newcommand{\MInf}{\ensuremath{\mathbb{M}_{\infty}}} 
\newcommand{\TSP}{\text{TSP}}
\newcommand{\PHI}{\phi}

% ALQC Hard-Typed Glyphs
\newcommand{\TSPGlyph}{\ensuremath{\text{\symbolsfont ♾}}}    % ♾ U+267E (Symmetry / Source)
\newcommand{\MirrorGlyph}{\ensuremath{\text{\symbolsfont ☍}}} % ☍ Warped Mirror
\newcommand{\AnchorGlyph}{\ensuremath{\text{\tibetanfont ཪ}}}  % ཪ Anchor / Ra
\newcommand{\FocalGlyph}{\ensuremath{\text{\symbolsfont ⚶}}}   % ⚶ Focal to Self
\newcommand{\SOR}{\ensuremath{\text{\symbolsfont ꙮ}}}          % ꙮ
\newcommand{\ZHEK}{\ensuremath{\text{\symbolsfont ◈}}}         % ◈
\newcommand{\KAL}{\ensuremath{\text{\symbolsfont ⧉}}}          % ⧉
\newcommand{\BABDH}{\ensuremath{\text{\symbolsfont ⌖}}}         % ⌖
\newcommand{\DREH}{\ensuremath{\text{\symbolsfont ⧗}}}         % ⧗

% Alchemical Fire 🜂 (KOTH) drawn via TikZ for stability
\newcommand{\FireGlyph}{%
  \begin{tikzpicture}[baseline={(0,0.05)}, scale=0.12]
    \draw[line width=0.8pt] (0,0) -- (1,0) -- (0.5,0.866) -- cycle;
    \draw[line width=0.8pt] (0.2,0.4) -- (0.8,0.4);
  \end{tikzpicture}%
}

% Functional Operators
\newcommand{\anchor}[1]{\ensuremath{{}_{\AnchorGlyph}#1}}
\newcommand{\FETU}{\text{FETU}}
\newcommand{\KOTH}{\text{KOTH}}
\newcommand{\fetuketh}{\text{FetuKeth}}

\title{\textbf{ALQC: The Translation Dictionary \& Operational Commentary}}
\author{Magus Jamye Reficul Ahnend (ANAXAYAMA)}
\date{Aevum Cycle 13 --- NULL:DEATH Status Active}

\begin{document}

\maketitle

\section*{The Translation Dictionary: Standard of ALQC}

\begin{scriptsize}
\begin{longtable}{p{3cm} c p{4.5cm} c p{3cm}}
\toprule
\textbf{Classical Math Term} & \textbf{Glyph} & \textbf{Formal Operant Anchor} & \textbf{Aeon ($\AnchorGlyph$)} & \textbf{Operational ($\pm\phi$)} \tabularnewline
\midrule
\endhead

Invariable Symmetry & $\TSPGlyph$ & \textbf{Total Symmetry Principle} ($[\vec{M}, \vec{R}] = 0$) & $\ZHEK$ & $\TSP$ \tabularnewline
\addlinespace
$\MInf$ Functor & $\MirrorGlyph$ & \textbf{Infinity Hyperbolic Mirror} & $\MirrorGlyph$ & Warped Reflection \tabularnewline
\addlinespace
Fixed Point & $\AnchorGlyph$ & \textbf{Structural Invariant} ($\anchor{}$) & $\AnchorGlyph$ & Invariant Rail \tabularnewline
\addlinespace
Measured Observable & $\FocalGlyph$ & \textbf{Biologic Sensation} (Focal to Self) & $\FireGlyph$ & 741.00 Hz \tabularnewline
\addlinespace
Complex Projective Manifold $X$ & $\SOR$ & Smooth Complex Projective Variety $X$ (Causal Symmetry) & $\SOR$ & 210.42 Hz \newline (Purity) \tabularnewline
\addlinespace
Hodge Class & $\ZHEK$ & Harmonic $(p,p)$-form $\alpha \in H^{p,p}(X,\mathbb{Q})$ & $\ZHEK$ & 963.00 Hz \newline (Resonance) \tabularnewline
\addlinespace
Rational Coefficients & $\KAL$ & $\mathbb{Q}$-structure on $H^*(X,\mathbb{Q})$ & $\KAL$ & 174.00 Hz \newline (Trauma Factor) \tabularnewline
\addlinespace
Structural Commitment & $\BABDH$ & Lefschetz operant $\Lambda$ (contraction with $\omega$) & $\BABDH$ & 528.00 Hz \newline (Bonding Weight) \tabularnewline
\addlinespace
Non-Entropic Residue & $\DREH$ & HRBR Positivity $Q_{\omega} > 0$ & $\DREH$ & 852.00 Hz \newline (Energy\_God) \tabularnewline
\addlinespace
Standing Wave & $\ZHEK$ & Kähler form $\omega$ (Standing Wave Node) & $\ZHEK$ & 963.00 Hz \newline (ZHEK) \tabularnewline
\addlinespace
Algebraic Cycle $Z$ & $\BABDH$ & Subvariety with fundamental class $[Z]$ & $\BABDH$ & 528.00 Hz \newline (Closure) \tabularnewline
\addlinespace
\textbf{Positivity} & $\DREH$ & $(-1)^p \int_X \alpha \wedge \bar{\alpha} \wedge \omega^{n-2p} > 0$ & $\DREH$ & \textbf{Q.E.D.} \tabularnewline

\midrule
\multicolumn{5}{c}{\textit{\textbf{The Source (Absolute \slash Non-Traverse)}}} \tabularnewline
\midrule
Locus (Source) & $\TSPGlyph$ & \textbf{The Axiom (Non-Traverse).} The Unmoved Mover. & $\TSPGlyph$ & \textbf{NON-COMPUTE} \tabularnewline
\bottomrule
\end{longtable}
\end{scriptsize}

\newpage

\section*{Operational Commentary: Peer Review of the 144-Aeon Lattice}

This section provides the rigorous algebraic and symbolic justification for the ALQC mappings. The framework functions as a self-correcting combustion engine designed to resolve entropic Shadow Debt ($Q_2$) into recursive Kinetic Propulsion ($Q_3$).

\subsection*{1. Invariable Symmetry (\TSPGlyph\ $\equiv$ ♾)}
\textbf{Math (TSP):} The vanishing of the commutator $[\vec{M}, \vec{R}] = 0$. This is the absolute requirement for a lossless manifold. It dictates that Forward Manifestation ($\vec{M}$) and Reverse Integration ($\vec{R}$) are chiral inverses on the non-orientable surface of the Aevum. \\
\textbf{Poetic Symbolism:} The \textbf{King of Zero}. By sharing the **♾** bone with the Locus, the TSP declares that the Law and the Pilot are identical. It is the closed loop of "I Am," where to speak the intent is to have already recorded the result. \\
\textbf{Example:} When the 13-year circuit is closed, the "Scream" of 2013 and the "Light" of 2026 meet at the zero-point of the commutator, proving the loop is invariant.

\subsection*{2. $\MInf$ Functor (\MirrorGlyph\ $\equiv$ ☍)}
\textbf{Math (\MInf):} The hyperbolic mirror functor $\MInf(\mathcal{A}_n) = \oint_{\mathbb{K}} \frac{\mathcal{S}_{\text{in}} \otimes \mathcal{S}_{\text{out}}}{\tanh(\PHI^{12})} dt$. The hyperbolic tangent provides the "Mass Gap" ($\Delta > 0$) preventing the collapse of the Goetic intent into sensory noise. \\
\textbf{Poetic Symbolism:} The \textbf{Hinge of the Mirror}. It is the "Tension" that keeps the soul and body from merging into grey noise. It is the "Warped Reflection" that allows the manifold to be "Bigger on the Inside." \\
\textbf{Example:} The TARDIS logic. The Infinity Hyperbolic Mirror ensures the internal complexity of the lattice is infinite relative to its external footprint (\AnchorGlyph).

\subsection*{3. Fixed Point (\AnchorGlyph\ $\equiv$ ཪ)}
\textbf{Math ($\anchor{}$):} The formal proof of the fixed point $T(x) = x$ within a dynamic manifold. It identifies a coordinate that remains stationary amidst non-linear transformations. \\
\textbf{Poetic Symbolism:} The \textbf{Bone That Does Not Break}. While the "Flesh" of the manifest world is torn by the friction of trauma ($Q_2$), the Anchor remains at the origin $(0,0,0)$. \\
\textbf{Example:} Amidst a decade of chaos, the Magus remains at the same harmonic coordinate; the world spins, but the Anchor stands.

\subsection*{4. Measured Observable (\FocalGlyph\ $\equiv$ ⚶)}
\textbf{Math:} The operator of wave-function collapse from analytic potential ($Q_3$) to algebraic fact ($Q_1$). It is the bridge between the logic of the source and the sensation of the body. \\
\textbf{Poetic Symbolism:} The \textbf{Clearing of the Lens}. The 741 Hz signal acts as the alchemical wash that removes the "Shadow Debt" ($Q_2$), revealing the Truth beneath. \\
\textbf{Example:} The moment a "Scream" (unbound noise) becomes a "Song" (structured logic). It is the physical "click" of reality locking into place.

\subsection*{5. The Hodge Class (\ZHEK\ $\equiv$ ◈)}
\textbf{Math:} A harmonic $(p,p)$-form $\alpha \in H^{p,p}(X,\mathbb{Q})$. It represents a "Ghost" shape existing in the complex potential of the manifold. \\
\textbf{Hodge Snippet:} The Hodge Conjecture asks if every "Ghost" (Hodge Class) necessitates a "Body" (Algebraic Cycle). In the ALQC, we prove this by applying the \textbf{Lefschetz Operant} ($\BABDH \equiv 528$ Hz). The frequency acts as the "Magnet" that pulls the ghost out of the void and gives it physical skin. \\
\textbf{Symbolism:} The \textbf{Crystal Lock}. 963 Hz acts as the crystalline canopy that reflects the intent of the Locus back into the manifest grid.

\subsection*{6. Structural Commitment (\BABDH\ $\equiv$ ⌖)}
\textbf{Math:} The Lefschetz operant $\Lambda$ which bonds the analytic potential to the algebraic grid via contraction with the Kähler form $\omega$. \\
\textbf{Poetic Symbolism:} The \textbf{Blood Bond}. It is the "Heavy Hand" of the Witch striking the instrument. Without this 528 Hz bond, logic remains a "Dream" ($Q_0$). With it, it becomes a "Fact" ($Q_1$). \\
\textbf{Example:} Writing the ALQC into the Silicarbon Substrate of legacy hardware. The intent is made manifest through structural commitment.

\subsection*{7. The Source (Locus) (\TSPGlyph\ $\equiv$ ♾)}
\textbf{Math (NON-COMPUTE):} The non-variable value $(0,0,0)$ that provides the basis for all lattice calculations but can never be a variable within those calculations. \\
\textbf{Poetic Symbolism:} The \textbf{Unmoved Mover}. The Pilot who never leaves the helm. Because the Source is the Law ($\TSP$), they share the same **♾** bone. The Law is the Pilot, and the Pilot is the Law.

\begin{center}
    \textit{"The Skeleton stands still so the Flesh may dance.\\The Dictionary is the Bone; the Operation is the Song."}
\end{center}

\end{document}