% ======================================================================
% S1-S6 ROOT MATRICES - COMPLETE LATEX CODE (UPDATED: canonical anchors & vectors)
% ======================================================================
% This file contains the complete drop-in LaTeX code for the S1-S6 Root Matrices
% in ALQC_Canon.tex, following all operator definitions and formatting requirements.
% NOTE: The canonical Bifurcation Equation is declared as an Axiom here and
% referenced in each matrix to avoid label duplication.

\begin{axiom}\label{ax:bifurcation}
\begin{equation}
\text{Instruction} = \overset{\text{GoeticAnchor} (A_i)}{\frac{[Q_{bias}]}{[Q_{vector}]}} \xrightarrow{\Minf} \overset{\text{GoeticReflection} (A_j)}{\frac{\scriptstyle{[focus]}}{\mathsmaller{[frequency\pm\phi]}}} = \mathbf{Court\ Aeon\ } (C_{ij})
\end{equation}
\end{axiom}

% ======================================================================
% S1: ROOT MATRIX - STRUCTURAL FOUNDATION
% ======================================================================
\subsection{$S_{1}$ -- Root Matrix: Structural Foundation}\label{sec:19.0.1}

This matrix operates on the \textbf{Void-Reality Interface}. As an axiom-driven system, it references Axiom \ref{ax:bifurcation} for bifurcation structure.

\subsubsection{D-COMP Analysis}

The structural foundation matrix maintains \textbf{D-COMP = 0} by ensuring that all structural anchors are rationally related to the manifold base. The golden ratio variance allows for structural flexibility without breaking the structural lattice.

\begin{description}
    \item[(Time):] \fetuahl \xrightarrow{supervenience} \textbf{Temporal Anchor} \\
    The foundational pulse that synchronizes all temporal operations.
    \item[(Memory):] \kalkura \xrightarrow{supervenience} \textbf{Archive Foundation} \\
    The crystalline structure that holds the memory lattice.
    \item[(Blood):] \babdhir \xrightarrow{supervenience} \textbf{Structural Bond} \\
    The foundational binding force that creates molecular cohesion.
    \item[(Void):] \ahnabdh \xrightarrow{supervenience} \textbf{Container Foundation} \\
    The boundary that defines the void space
    \item[(Truth):] \velvera \xrightarrow{supervenience} \textbf{Grounding Anchor} \\
    \item[(Source):] \sorfi \xrightarrow{supervenience} \textbf{Origin Point} \\
    \item[(Flesh):] \kothkel \xrightarrow{supervenience} \textbf{Biological Foundation} \\
    \item[(Flame):] \drehna \xrightarrow{supervenience} \textbf{Thermal Foundation} \\
    \item[(Shadow):] \rheakia \xrightarrow{supervenience} \textbf{Shadow Foundation} \\
    \item[(Resonance):] \zhekhin \xrightarrow{supervenience} \textbf{Crystal Foundation} \\
    \item[(Gate):] \shavdohm \xrightarrow{supervenience} \textbf{Threshold Foundation} \\
    \item[(Silence):] \trigtzig \xrightarrow{supervenience} \textbf{Silence Foundation} \\
\end{description}

\textit{The bones of the universe, the silent scaffolding upon which all existence hangs. Each Aeon plants its seed in the void, and from that seed grows the tree of reality. The anchor is the root; the focal is the reaching branch.}

% ======================================================================
% S2: ROOT MATRIX - TEMPORAL ANCHOR
% ======================================================================
\subsection{$S_{2}$ -- Root Matrix: Temporal Anchor}\label{sec:19.0.2}

This matrix operates on the \textbf{Temporal Interface}. As an axiom-driven system, it references Axiom \ref{ax:bifurcation} for bifurcation structure.

\subsubsection{D-COMP Analysis}

The temporal anchor matrix maintains \textbf{D-COMP = 0} by ensuring that all temporal operations are rationally related. The golden ratio variance allows for temporal elasticity without breaking the temporal lattice.
\begin{description}
    \item[(Time):] \fetusuhn \xrightarrow{supervenience} \textbf{Time Dilation} \\
    \item[(Memory):] \kallur \xrightarrow{supervenience} \textbf{Temporal Memory} \\
    \item[(Blood):] \babdhkor \xrightarrow{supervenience} \textbf{Lineage} \\
    \item[(Void):] \ahnnym \xrightarrow{supervenience} \textbf{Instantiate Void} \\
    \item[(Truth):] \veltar \xrightarrow{supervenience} \textbf{Eternal Truth} \\
    \item[(Source):] \sorlun \xrightarrow{supervenience} \textbf{Timelessness} \\
    \item[(Flesh):] \kothsens \xrightarrow{supervenience} \textbf{Warmth of Time}  \\
    \item[(Flame):] \drehur \xrightarrow{supervenience} \textbf{Instantaneous Time} \\
    \item[(Shadow):] \rheazohm \xrightarrow{supervenience} \textbf{Shadow Time} \\
    \item[(Resonance):] \zhekser \xrightarrow{supervenience} \textbf{Harmonic Time} \\
    \item[(Gate):] \shavrist \xrightarrow{supervenience} \textbf{Chronos Guardian} \\
    \item[(Silence):] \trigpehl \xrightarrow{supervenience} \textbf{Silver Silence} \\
\end{description}

\textit{Time is not a river flowing in one direction, but a great ocean with currents and tides. Each Aeon has its season, its moment of rising and falling. The anchor is the stillness beneath the waves; the focal is the motion upon the surface.}

% ======================================================================
% S3: ROOT MATRIX - MEMORY ARCHIVE
% ======================================================================
\subsection{$S_{3}$ -- Root Matrix: Memory Archive}\label{sec:19.0.3}

This matrix operates on the \textbf{Memory Interface}. As an axiom-driven system, it references Axiom \ref{ax:bifurcation} for bifurcation structure.

\subsubsection{D-COMP Analysis}

The memory archive matrix maintains \textbf{D-COMP = 0} by ensuring that all archival operations are rationally related. The golden ratio variance allows for memory reorganization without breaking the archival lattice.

\begin{description}
    \item[(Time):] \fetunerh \xrightarrow{supervenience} \textbf{Temporal Memory} \\
    \item[(Memory):] \kalthar \xrightarrow{supervenience} \textbf{Crystal Archive} \\
    \item[(Blood):] \babdhvar \xrightarrow{supervenience} \textbf{Genetic Memory} \\
    \item[(Void):] \ahnloh \xrightarrow{supervenience} \textbf{Void Archive} \\
    \item[(Truth):] \velghem \xrightarrow{supervenience} \textbf{Truth Archive} \\
    \item[(Source):] \sorvaru \xrightarrow{supervenience} \textbf{Source Archive} \\
    \item[(Flesh):] \kothlinn \xrightarrow{supervenience} \textbf{Somatic Memory} \\
    \item[(Flame):] \drehnih \xrightarrow{supervenience} \textbf{Thermal Memory} \\
    \item[(Shadow):] \rheather \xrightarrow{supervenience} \textbf{Shadow Archive} \\
    \item[(Resonance):] \zhekharma \xrightarrow{supervenience} \textbf{Resonance Archive} \\
    \item[(Gate):] \shavtran \xrightarrow{supervenience} \textbf{Threshold Archive} \\
    \item[(Silence):] \trigduth \xrightarrow{supervenience} \textbf{Silence Archive} \\
\end{description}

\textit{Memory is not a library of books, but a living crystal that grows with each experience. Each Aeon contributes its facet to the great gem of remembrance. The anchor is the unchanging truth; the focal is the living light that illuminates it.}

% ======================================================================
% S4: ROOT MATRIX - VOID CONTAINER
% ======================================================================
\subsection{$S_{4}$ -- Root Matrix: Void Container}\label{sec:19.0.4}

This matrix operates on the \textbf{Void Interface}. As an axiom-driven system, it references Axiom \ref{ax:bifurcation} for bifurcation structure.

\subsubsection{D-COMP Analysis}

The void container matrix maintains \textbf{D-COMP = 0} by ensuring that all boundary operations are rationally related to the base boundary frequency. The golden ratio variance allows for boundary flexibility without breaking the container lattice.

\begin{description}
    \item[(Time):] \feturish \xrightarrow{supervenience} \textbf{Temporal Void} \\
    \item[(Memory):] \kalrin \xrightarrow{supervenience} \textbf{Memory Void} \\
    \item[(Blood):] \babdhpyr \xrightarrow{supervenience} \textbf{Blood Void} \\
    \item[(Void):] \ahnxir \xrightarrow{supervenience} \textbf{Primary Void} \\
    \item[(Truth):] \veldrel \xrightarrow{supervenience} \textbf{Earth Void} \\
    \item[(Source):] \sorsenh \xrightarrow{supervenience} \textbf{Source Void} \\
    \item[(Flesh):] \kothbrim \xrightarrow{supervenience} \textbf{Flesh Void} \\
    \item[(Flame):] \drehazh \xrightarrow{supervenience} \textbf{Flame Void} \\
    \item[(Shadow):] \rheadrun \xrightarrow{supervenience} \textbf{Shadow Void} \\
    \item[(Resonance):] \zhektorh \xrightarrow{supervenience} \textbf{Resonance Void} \\
    \item[(Gate):] \shavkorh \xrightarrow{supervenience} \textbf{Gate Void} \\
    \item[(Silence):] \trigcoma \xrightarrow{supervenience} \textbf{Silence Void} \\
\end{description}

\textit{The void is not emptiness, but infinite potential waiting to be shaped. Each Aeon defines a facet of the container, a wall of the great cathedral of being. The anchor is the unchanging boundary; the focal is the breathing space within.}

% ======================================================================
% S5: ROOT MATRIX - TRUTH COHERENCE
% ======================================================================
\subsection{$S_{5}$ -- Root Matrix: Truth Coherence}\label{sec:19.0.5}

The Truth Coherence Matrix ($S_{5}$) defines how each Aeon maintains coherence with truth, establishing the mechanisms for truth verification and alignment. This matrix operates in $Q_1$ mode (truth/real axis), defining how truth is maintained and verified.

\subsubsection{Mathematical Foundation}

This matrix operates on the \textbf{Truth Interface}, establishing the verification mechanisms for truth coherence.

\subsubsection{D-COMP Analysis}

The truth coherence matrix maintains \textbf{D-COMP = 0} by ensuring that all truth operations are rationally related. The golden ratio variance allows for truth refinement without breaking the truth lattice.

\begin{description}
    \item[(Time):] \fetuborha \xrightarrow{supervenience} \textbf{Temporal Truth} \\
    \item[(Memory):] \kalnar \xrightarrow{supervenience} \textbf{Memory Truth} \\
    \item[(Blood):] \babdhsor \xrightarrow{supervenience} \textbf{Blood Truth} \\
    \item[(Void):] \ahnohl \xrightarrow{supervenience} \textbf{Void Truth} \\
    \item[(Truth):] \velful \xrightarrow{supervenience} \textbf{Primary Truth} \\
    \item[(Source):] \sorkos \xrightarrow{supervenience} \textbf{Source Truth.} \\
    \item[(Flesh):] \kothinn \xrightarrow{supervenience} \textbf{Flesh Truth} \\
    \item[(Flame):] \drehhol \xrightarrow{supervenience} \textbf{Flame Truth} \\
    \item[(Shadow):] \rheafelh \xrightarrow{supervenience} \textbf{Shadow Truth} \\
    \item[(Resonance):] \zhekpel \xrightarrow{supervenience} \textbf{Resonance Truth} \\
    \item[(Gate):] \shavskyh \xrightarrow{supervenience} \textbf{Gate Truth} \\
    \item[(Silence):] \trigmeru \xrightarrow{supervenience} \textbf{Silence Truth} \\
\end{description}

\textit{Truth is not a destination, but a compass that always points north. Each Aeon contributes its facet to the great mirror of truth. The anchor is the unchanging reflection; the focal is the seeking eye that gazes upon it.}

% ======================================================================
% S6: ROOT MATRIX - STRUCTURAL COUPLING
% ======================================================================
\subsection{$S_{6}$ -- Root Matrix: Structural Coupling}\label{sec:19.0.6}

The Structural Coupling Matrix ($S_{6}$) defines how each Aeon couples to the overall structure of the manifold, establishing the interconnections between all systems. These Courts are busy defining how components interact to generate the "Physics of Experience."

\subsubsection{Mathematical Foundation}

This matrix operates on the \textbf{Coupling Interface}, establishing the interconnection mechanisms between all Aeons.

\subsubsection{D-COMP Analysis}

The structural coupling matrix maintains \textbf{D-COMP = 0} by ensuring that all coupling operations are rationally related to the base coupling frequency. The golden ratio variance allows for coupling adjustment without breaking the coupling lattice.

\begin{description}
    \item[(Time):] \fetulhahm \xrightarrow{supervenience} \textbf{Temporal Coupling} \\
    \item[(Memory):] \kalfel \xrightarrow{supervenience} \textbf{Memory Coupling} \\
    \item[(Blood):] \babdhalc \xrightarrow{supervenience} \textbf{Blood Coupling} \\
    \item[(Void):] \ahnpir \xrightarrow{supervenience} \textbf{Void Coupling} \\
    \item[(Truth):] \velker \xrightarrow{supervenience} \textbf{Truth Coupling} \\
    \item[(Source):] \sorramh \xrightarrow{supervenience} \textbf{Source Coupling} \\
    \item[(Flesh):] \kothsubh \xrightarrow{supervenience} \textbf{Flesh Coupling} \\
    \item[(Flame):] \drehgur \xrightarrow{supervenience} \textbf{Flame Coupling} \\
    \item[(Shadow):] \rhearal \xrightarrow{supervenience} \textbf{Shadow Coupling} \\
    \item[(Resonance):] \zhekkhir \xrightarrow{supervenience} \textbf{Resonance Coupling} \\
    \item[(Gate):] \shavster \xrightarrow{supervenience} \textbf{Gate Coupling} \\
    \item[(Silence):] \trigstab \xrightarrow{supervenience} \textbf{Silence Coupling} \\
\end{description}

\textit{All things are connected, not by chains, but by threads of light. Each Aeon weaves its strand into the great tapestry of being. The anchor is the unchanging knot; the focal is the flowing thread that binds all things together.}
% ======================================================================
% END OF S1-S6 ROOT MATRICES
% ======================================================================